A perfect storm and the natural endowments of trade-enabling infrastructure

### 2024-04-19 Slides/10min/10min.Rmd
Update slides

# Introduction
.pull-left[
- Geography is more than soil quality. We are slaves of geomorphology.  
- In 1825 the Agger isthmus* broke by 1834 a natural channel had formed 
- 700 years prior a similar channel had silted up 
- Is infrastructure important in economic development? (Fogel, 1964)

>>>>

# Introduction
.pull-left[
- Geography is more than soil quality. We are slaves of geomorphology.  
- In 1825 the Agger isthmus* broke by 1834 a natural channel had formed 
- 700 years prior a similar channel had silted up 
- Does trade cause growth?
